Spin canonical divisors of log stacky curves

### 2015-06-24 stacky_write_up/spin_cring.tex
include delta>0 in g=0 pf

\section{Genus Zero}
\label{sec:g_0}
Now we consider the genus zero case.
\todo{write intro}

\ssec{Genus Zero Effective}
\label{ssec:g_0_effective}

In this section, we examine the case $2\halfcan\sim K_\sx+\Delta$ 
when $\Delta$ is a non- zero effective divisor.  Using this, we can 
reduce to looking at effective stacky divisors.  Then, applying a 
result for general effective $\mathbf{Q}$ divisors, we deduce that $
R_{\halfcan}$ is generated in degrees up to $e=\max{e_i}$ with 
relations generated up to degree $2e$ with initial terms quadratic 
in the generators.  We also demonstrate that these bounds are tight 
up to \todo{insert how tight they are}.

We have Lemma ~\ref{lem:minimal_quadratic}.
\todo{fill in hole here, with adding points too}

\begin{lem}\label{lem:add_point_effective_divisor_deg_1_but_not_deg_2_generators}
Let $2\halfcan=K_X$ of a non-stacky curve $X$ such that $h^0(X, \halfcan) > 0$.  Then for any point $P$, 
\[
	H^0(X, \halfcan+P)=H^0(X,\halfcan).
\]
\end{lem}
\begin{proof}
\todo{add proof}
\end{proof}

\ssec{Genus Zero Non-effective}
\label{ssec:g_0_non_effective}
In this section, we will prove that if $(\sx , 0, L)$ is a spin curve,
so that $\sx$ has signature $\sigma = (0; e_1, \ldots , e_r; 0)$, then
$R(\sx , 0, L)$ is generated in degree at most $e := \max(5, e_1, \ldots,
e_r)$ with relations generated in degree at most $2e$, so long as $\sigma$
does not lie in a finite list of exceptions. This is proven in
Subsection ~\ref{ssec:g_0_main}. The proof is a rather
involved induction. In Subsections ~\ref{ssec:g_0_ram_pts},
~\ref{ssec:g_0_ram_orders} \todo{fix} we prove inductive theorems, and in
Subsection ~\ref{ssec:g_0_base} we check the base cases of the
induction. Finally, in Subsection ~\ref{ssec:g_0_exceptional} we
list out the exceptional cases.

@@

\begin{proof}
If $\sx$ has no stacky points, then we have the classical
case which is done in Chapter 4 of Voight and Zureick-Brown
\cite{vzb:stacky}.

Now let us consider the case when $\delta \geq 2$. In this case,
$\halfcan$ is an effective divisor. \todo{need to do this case}

>>>>

\section{Genus Zero}
\label{sec:g_0}
We will prove that if $(\sx , 0, \halfcan)$ is a spin curve, so
that $\sx$ has signature $\sigma = (0; e_1, \ldots , e_r; \delta)$,
then $R(\sx , \Delta, L)$ is generated in degree at most $e := \max(
5, e_1, \ldots, e_r)$ with relations generated in degree at most $2e
$, so long as $\sigma$ does not lie in a finite list of exceptions.

There are two main cases: when $\delta \geq 2$ and when $\delta = 0$
 (note that $\delta$ must be odd or zero because $\halfcan \in \text
{ Div } \sx$). In the first case, $\deg \lfloor \halfcan \rfloor
\geq 0$ so the result directly follows from Lemma
~\ref{rem:deg1_sat_ind}. When $\delta = 0$, this is not necessarily
true so the proof is a rather involved induction using Lemma
~\ref{lem:sat_three_ induction} and Theorem ~\ref{thm:ram_order_ind}.
The remainder of this section is dedicated to characterizing the
saturations ( Subsection ~\ref{ssec:g_0_saturation}), inductive
base cases ( Subsection ~\ref{ssec:g_0_base}), and exceptional
cases (Subsection ~\ref{ssec:g_0_exceptional}) when $\delta = 0$
before proving the main theorem in full for all $\delta$ in
Subsection ~\ref{ssec:g_0_ main}.

@@

\begin{proof}
If $\sx$ has no stacky points, then we have the classical
case which is done in Voight and Zureick-Brown ~\cite[Section 4.2]
{vzb:stacky}.

Now let us consider the case when $\delta \geq 2$. In any such case,
$\lfloor \halfcan \rfloor$ is an effective divisor and the conditions
of Lemma ~\ref{rem:deg1_sat_ind} are satisfied. Thus, we can apply
the lemma inductively on the classical case with no stacky points
to get that $R(\sx, \Delta, \halfcan)$ is generated up to degree $e$
with relations generated up to degree $2e$.
